Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks

### 2020-03-11 paper/paper.tex
wrote some paper

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{graphicx}

@@

@@

	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
	Pavia University dataset, the Pavia Center dataset, the Salinas Valley dataset and the Salinas A dataset, which is
	a small subset of the Salinas Valley dataset.
	The first three of them are relatively large dataset and the last one is relatively small.
	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
	Here follows the brief introduction of the four dataset.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{xcolor}

@@

\newcommand\crule[3][black]{\textcolor{#1}{\rule{#2}{#3}}}
%color map definition
%pavia c
\definecolor{paviaU0}{RGB}{0, 0, 0}
\definecolor{paviaU1}{RGB}{219, 94, 86}
\definecolor{paviaU2}{RGB}{219, 183, 86}
\definecolor{paviaU3}{RGB}{167, 219, 86}
\definecolor{paviaU4}{RGB}{86, 219, 94}
\definecolor{paviaU5}{RGB}{86, 219, 183}
\definecolor{paviaU6}{RGB}{86, 167, 219}
\definecolor{paviaU7}{RGB}{94, 86, 219}
\definecolor{paviaU8}{RGB}{183, 86, 219}
\definecolor{paviaU9}{RGB}{219, 86, 167}
%pavia c
\definecolor{pavia0}{RGB}{0, 0, 0}
\definecolor{pavia1}{RGB}{219, 94, 86}
\definecolor{pavia2}{RGB}{219, 183, 86}
\definecolor{pavia3}{RGB}{167, 219, 86}
\definecolor{pavia4}{RGB}{86, 219, 94}
\definecolor{pavia5}{RGB}{86, 219, 183}
\definecolor{pavia6}{RGB}{86, 167, 219}
\definecolor{pavia7}{RGB}{94, 86, 219}
\definecolor{pavia8}{RGB}{183, 86, 219}
\definecolor{pavia9}{RGB}{219, 86, 167}
%salinas
\definecolor{salinas_corrected0}{RGB}{0, 0, 0}
\definecolor{salinas_corrected1}{RGB}{219, 94, 86}
\definecolor{salinas_corrected2}{RGB}{219, 144, 86}
\definecolor{salinas_corrected3}{RGB}{219, 194, 86}
\definecolor{salinas_corrected4}{RGB}{194, 219, 86}
\definecolor{salinas_corrected5}{RGB}{145, 219, 86}
\definecolor{salinas_corrected6}{RGB}{95, 219, 86}
\definecolor{salinas_corrected7}{RGB}{86, 219, 127}
\definecolor{salinas_corrected8}{RGB}{86, 219, 177}
\definecolor{salinas_corrected9}{RGB}{86, 211, 219}
\definecolor{salinas_corrected10}{RGB}{86, 161, 219}
\definecolor{salinas_corrected11}{RGB}{86, 111, 219}
\definecolor{salinas_corrected12}{RGB}{111, 86, 219}
\definecolor{salinas_corrected13}{RGB}{160, 86, 219}
\definecolor{salinas_corrected14}{RGB}{210, 86, 219}
\definecolor{salinas_corrected15}{RGB}{219, 86, 178}
\definecolor{salinas_corrected16}{RGB}{219, 86, 128}
%salinas a
\definecolor{salinasA_corrected0}{RGB}{0, 0, 0}
\definecolor{salinasA_corrected1}{RGB}{219, 94, 86}
\definecolor{salinasA_corrected2}{RGB}{211, 219, 86}
\definecolor{salinasA_corrected3}{RGB}{86, 219, 94}
\definecolor{salinasA_corrected4}{RGB}{86, 211, 219}
\definecolor{salinasA_corrected5}{RGB}{94, 86, 219}
\definecolor{salinasA_corrected6}{RGB}{219, 86, 211}

@@

	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
	Pavia University dataset, the Pavia Center dataset, the Salinas Valley dataset and the Salinas A dataset, which is
	a small subset of the Salinas Valley dataset.
	The first three of them are relatively large dataset and the last one is relatively small.
	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
	Here follows the brief introduction of the four dataset.
	\begin{enumerate}[1)]
		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
		campaign over Pavia, northern Italy.
		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
		Pavia Centre is a 1096*1096 pixels image, and Pavia University is 610*610 pixels, but some of the samples in
		both images contain no information and have to be discarded before the analysis, so the final picture size is
		1096*715 and 610*340.
		The geometric resolution is 1.3 meters.
		Both image has 9 different ground truth classes each(see table\ref{paviagt}).
		\begin{table}[h]
			\centering
			\begin{tabular}{|c|c|}
				\hline
				\textbf{PAVIA CENTER}    & \textbf{PAVIA UNIVERSITY}\\
				\hline
				\includegraphics[width=0.4\textwidth]{pic/pavia_gt.eps}&
				\includegraphics[width=0.4\textwidth]{pic/paviaU_gt.eps}\\
				\hline
				\begin{tabular}{ccc}
					\footnotesize
					\textit{color}&\textit{land-cover type}&\textit{number}\\
					\hline
					\crule[pavia1]{0.02\textwidth}{0.02\textwidth} &Water &824    \\
					\crule[pavia2]{0.02\textwidth}{0.02\textwidth} &Trees &820    \\
					\crule[pavia3]{0.02\textwidth}{0.02\textwidth} &Asphalt &816    \\
					\crule[pavia4]{0.02\textwidth}{0.02\textwidth} &Self-Blocking Bricks &808    \\
					\crule[pavia5]{0.02\textwidth}{0.02\textwidth} &Bitumen &808    \\
					\crule[pavia6]{0.02\textwidth}{0.02\textwidth} &Tiles &1260   \\
					\crule[pavia7]{0.02\textwidth}{0.02\textwidth} &Shadows &476    \\
					\crule[pavia8]{0.02\textwidth}{0.02\textwidth} &Meadows &824    \\
					\crule[pavia9]{0.02\textwidth}{0.02\textwidth} &Bare Soil &820    \\
				\end{tabular}&
				\begin{tabular}{ccc}
					\footnotesize
					\textit{color}&\textit{land-cover type}&\textit{number}\\
					\hline
					\crule[paviaU1]{0.02\textwidth}{0.02\textwidth} &Asphalt &6631   \\
					\crule[paviaU2]{0.02\textwidth}{0.02\textwidth} &Meadows &18649  \\
					\crule[paviaU3]{0.02\textwidth}{0.02\textwidth} &Gravel &2099   \\
					\crule[paviaU4]{0.02\textwidth}{0.02\textwidth} &Trees &3064   \\
					\crule[paviaU5]{0.02\textwidth}{0.02\textwidth} &Painted metal sheets &1345   \\
					\crule[paviaU6]{0.02\textwidth}{0.02\textwidth} &Bare Soil &5029   \\
					\crule[paviaU7]{0.02\textwidth}{0.02\textwidth} &Bitumen &1330   \\
					\crule[paviaU8]{0.02\textwidth}{0.02\textwidth} &Self-Blocking Bricks &3682   \\
					\crule[paviaU9]{0.02\textwidth}{0.02\textwidth} &Shadows &947    \\
				\end{tabular}\\
				\hline
			\end{tabular}
			\caption{Number of samples in two Pavia scene dataset.}
			\label{paviagt}
		\end{table}
		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
		California, and is characterized by high spatial resolution (3.7-meter pixels).
		The Salinas Valley dataset is a 512*217 pixels image, and the Salinas A is a subset of the Salinas Valley
		containing 86*83 pixels.
		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
		bands left in both of the tow dataset.
		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes(see
		table\ref{salinas_gt}).
		\begin{table}[h]
			\centering
			\begin{tabular}{|c|c|}
				\hline
				\textbf{SALINAS VALLEY}  & \textbf{SALINAS A}\\
				\hline
				\includegraphics[width=0.4\textwidth]{pic/salinas_gt.eps}&
				\includegraphics[width=0.4\textwidth]{pic/salinasA_gt.eps}\\
				\hline
				\begin{tabular}{ccc}
					\footnotesize
					\textit{color}&\textit{land-cover type}&\textit{number}\\
					\hline
					\crule[salinas_corrected1]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-1 &2009  \\
					\crule[salinas_corrected2]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-2 &3726  \\
					\crule[salinas_corrected3]{0.02\textwidth}{0.02\textwidth} &Fallow &1976  \\
					\crule[salinas_corrected4]{0.02\textwidth}{0.02\textwidth} &Fallow rough plow &1394  \\
					\crule[salinas_corrected5]{0.02\textwidth}{0.02\textwidth} &Fallow smooth &2678  \\
					\crule[salinas_corrected6]{0.02\textwidth}{0.02\textwidth} &Stubble &3959  \\
					\crule[salinas_corrected7]{0.02\textwidth}{0.02\textwidth} &Celery &3579  \\
					\crule[salinas_corrected8]{0.02\textwidth}{0.02\textwidth} &Grapes untrained &11271  \\
					\crule[salinas_corrected9]{0.02\textwidth}{0.02\textwidth} &Soil vinyard develop &6203  \\
					\crule[salinas_corrected10]{0.02\textwidth}{0.02\textwidth} &Corn senesced green weeds &3278  \\
					\crule[salinas_corrected11]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-4wk &1068  \\
					\crule[salinas_corrected12]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-5wk &1927  \\
					\crule[salinas_corrected13]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-6wk &916  \\
					\crule[salinas_corrected14]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-7wk &1070  \\
					\crule[salinas_corrected15]{0.02\textwidth}{0.02\textwidth} &Vinyard untrained &7268  \\
					\crule[salinas_corrected16]{0.02\textwidth}{0.02\textwidth} &Vinyard vertical trellis &1807  \\
				\end{tabular}&
				\begin{tabular}{ccc}
					\footnotesize
					\textit{color}&\textit{land-cover type}&\textit{number}\\
					\hline
					\crule[salinasA_corrected1]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-1 &391  \\
					\crule[salinasA_corrected2]{0.02\textwidth}{0.02\textwidth} &Corn senesced green weeds &1343  \\
					\crule[salinasA_corrected3]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-4wk &616  \\
					\crule[salinasA_corrected4]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-5wk &1525  \\
					\crule[salinasA_corrected5]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-6wk &674  \\
					\crule[salinasA_corrected6]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-7wk &799  \\
					\\
					\\
					\\
					\\
					\\
					\\
					\\
					\\
					\\
					\\
				\end{tabular}\\
				\hline
			\end{tabular}
			\caption{Number of samples in the two Salinas scene dataset.}
			\label{salinas_gt}
		\end{table}
	\end{enumerate}
